Hydras \& Co.

### 2022-05-17 doc/epsilon0-chapter.tex
Revision book to page 82. deprecate a few symbols

This term would have been written \(\omega^1\times 2 + \omega^\omega \times 3\) in the usual mathematical notation. We note that the exponents of $\omega$ are not in the right (strictly decreasing) order.
Nevertheless, with the help of the order \texttt{lt} on \texttt{T1}, we are now able to characterize
the set of all well-formed ordinal terms:

@@

\paragraph*{\gaiasign}
\index{gaiabridge}{Type of well formed ordinal terms below $\epsilon_0$}
 The library~\href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge} defines a \gaia-compatible type \texttt{E0}.

@@

\vspace{4pt}
\noindent
\emph{From Module~\href{../theories/html/hydras.Epsilon0.T1.html\#succb}{Epsilon0.T1}}

@@

\paragraph*{\gaiasign}
\index{gaiabridge}{Limit and successor ordinals}
In \gaia, the boolean functions associated with limit and successor ordinals are called \texttt{T1limit} and \texttt{T1is\_succ}.

@@

The following lemma establishes the connection between the  function
\texttt{succ} and the Boolean predicate \texttt{succb}.

@@

\begin{exercise}[\gaiasign]
  Look for the \gaia-theorem which corresponds to \texttt{succb\_iff}.
\end{exercise}

>>>>

This term would have been written \(\omega^1\times 2 + \omega^\omega \times 3\) in the usual mathematical notation. We note that the exponents of $\omega$ are not in the right (strictly decreasing) order. The following boolean function determines whether a given ordinal term is well formed.

@@

\paragraph*{\gaiasign}
\index{gaiabridge}{Type of well formed ordinal terms below $\epsilon_0$}
 Our library~\href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge} defines also a type \texttt{E0} (which doesn't exist in \gaia-\texttt{ssete9}).

@@

\vspace{4pt}
\noindent
\emph{From Module~\href{../theories/html/hydras.Epsilon0.T1.html\#T1is_succ}{Epsilon0.T1}}

@@

\paragraph*{\gaiasign}
\index{gaiabridge}{Limit and successor ordinals}
In \gaia, the boolean functions associated with limit and successor ordinals are also called \texttt{T1limit} and \texttt{T1is\_succ}.

@@

The following lemma establishes the connection between the  function
\texttt{succ} and the Boolean predicate \texttt{T1is\_succ}.

@@

\begin{exercise}[\gaiasign]
  Look for the \gaia-theorem which corresponds to \texttt{T1is\_succ\_iff}.
\end{exercise}

### 2022-05-17 doc/ks-chapter.tex
Revision book to page 82. deprecate a few symbols

Note the use of \coq's \texttt{sig} type in the theorem's statement, which
relates the boolean function \texttt{limitb} defined on the \texttt{T1} data-type with a constructive view of the limit of a sequence: for any $\beta<\lambda$, we can compute an item of the canonical sequence of $\lambda$ which is greater than $\beta$.
We can also state directly that $\lambda$ is a (strict) least upper bound of the elements of its canonical sequence.

>>>>

Note the use of \coq's \texttt{sig} type in the theorem's statement, which
relates the boolean function \texttt{T1limit} defined on the \texttt{T1} data-type with a constructive view of the limit of a sequence: for any $\beta<\lambda$, we can compute an item of the canonical sequence of $\lambda$ which is greater than $\beta$.
We can also state directly that $\lambda$ is a (strict) least upper bound of the elements of its canonical sequence.

### 2022-05-17 doc/ordinal-chapter.tex
Revision book to page 82. deprecate a few symbols

If \texttt{OB} is presumed to be correct, then we may consider that \texttt{OA} ``inherits'' its correctness from the bigger notation system \texttt{OB}.

@@

following definition
(in ~\href{../theories/html/hydras.OrdinalNotations.ON_Generic.html}{ON\_Generic}).

>>>>

@@

\noindent
From~\href{../theories/html/hydras.OrdinalNotations.ON_Generic.html}{ON\_Generic}.
